Impact of grids and dynamical cores in CESM2.2 on the surface mass balance of the Greenland Ice Sheet

### 2022-03-24 arcticgrids.tex
new melt figure

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_violens.pdf}
\end{center}
\caption{.}
\label{fig:pointdiff}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_transect_obsperiod.pdf}
\end{center}
\caption{.}
\label{fig:trans}
\end{figure}

@@

\subsection{Impact of horizontal resolution on extremes}

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_composite_ge45N_JAN-PRECT.pdf}
\end{center}
\caption{.}
\label{fig:comp-mean}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_contours_diffRACMO_melt.pdf}
\end{center}
\caption{.}
\label{fig:melt}
\end{figure}

@@

%\begin{figure}[t]
%\begin{center}
%         \includegraphics[width=130mm]{figs/temp_violens.pdf}
%\end{center}
%\caption{.}
%\label{fig:pointdiff}
%\end{figure}

@@

%\begin{figure}[t]
%\begin{center}
%         \includegraphics[width=130mm]{figs/temp_transect_obsperiod.pdf}
%\end{center}
%\caption{.}
%\label{fig:trans}
%\end{figure}

@@

\subsection{Precipitation extremes}

@@

%\begin{figure}[t]
%\begin{center}
%         \includegraphics[width=130mm]{figs/temp_composite_ge45N_JAN-PRECT.pdf}
%\end{center}
%\caption{.}
%\label{fig:comp-mean}
%\end{figure}
